`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-05-15 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd
fix printing bug

```{r, results = 'asis'}
ref_celltype <- stringr::str_split(params$reference_name, "_")[1]
ref_type <- stringr::str_split(params$reference_name, "_")[2]

@@

glue::glue(
  "`inferCNV` was run with the following normal reference: `{params$reference_name}`.
  This reference contains all {ref_celltype} cells {reference_type_text}, excluding any which were also identified as tumor in the `cell-type-ewings` analysis module.
  "
)
```

>>>>

```{r, results = 'asis'}
ref_celltype <- stringr::str_split_1(params$reference_name, "_")[1]
ref_type <- stringr::str_split_1(params$reference_name, "_")[2]

@@

glue::glue(
  "`inferCNV` was run with the following normal reference: `{params$reference_name}`.
  This reference contains all {ref_text[[ref_celltype]]} cells {reference_type_text}, excluding any which were also identified as tumor in the `cell-type-ewings` analysis module.
  "
)
```
